\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{green}

\usepackage[scale=0.75]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}

% Personal data
\name{Thanh}{Hoang-Minh}
\title{Application for Machine Learning Engineer Position}
\address{Ho Chi Minh City}{}{Vietnam}
\phone[mobile]{+84~913~472~506}
\email{hmthanhgm@gmail.com}
\homepage{hmthanh.github.io}

\begin{document}
	
	% Letter recipient
	\recipient{Ahrefs}{Hiring Team}
	\date{\today}
	\opening{Dear Ahrefs Hiring Team,}
	\closing{Thank you for your consideration.}
	\enclosure[Attachment]{Curriculum Vitae}
	\makelettertitle
	
I am writing to apply for the Machine Learning Engineer position. The opportunity to work with Ahrefs SuperPod's top-tier computing infrastructure to push the boundaries of AI is incredibly compelling.

My expertise lies in the full-stack development of LLMs. I have hands-on experience fine-tuning large models (e.g., a 20B parameter model for MillionScope) using modern PEFT methods like \textbf{QLoRA} and \textbf{RLHF}. I am adept at optimizing and deploying these models for production using \textbf{SGLang}, \textbf{ONNX}, and \textbf{TensorRT}, directly aligning with your focus on inference latency and efficiency.

While my projects have operated on a smaller scale, they have provided a deep foundation in the core principles of efficient training and serving. I am confident in my ability to rapidly contribute to and learn from your large-scale distributed environment.

I am eager to discuss how my skills in turning research into production-ready AI can bring value to Ahrefs.


	
	
	\makeletterclosing
	
\end{document}
