\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{green}

\usepackage[scale=0.75]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}

% Personal data
\name{Thanh}{Hoang-Minh}
\title{Application for Senior Software Engineer Position}
\address{Ho Chi Minh City}{}{Vietnam}
\phone[mobile]{+84~913~472~506}
\email{hmthanhgm@gmail.com}
\homepage{hmthanh.github.io}

\begin{document}
	
	% Letter recipient
	\recipient{Speechify}{Hiring Team}
	\date{\today}
	\opening{Dear Speechify Hiring Team,}
	\closing{Thank you for your consideration.}
	\enclosure[Attachment]{Curriculum Vitae}
	\makelettertitle
	
	I am writing to apply for the \textbf{Senior Software Engineer} position at Speechify. The opportunity to contribute to a product that makes reading accessible through state-of-the-art TTS technology strongly aligns with my experience and interests.
	
	I'm creator of ParrotSpeech TTS (A vietnamese fine-tune of F5-TTS), experience fine-tuning GPT-OSS models, using quantization methods like QLoRA and deploying them in production environments. I am proficient in optimizing inference latency and cost through techniques such as ONNX export, and kernel-level optimizations.
	
	Additionally, I have extensive experience deploying high-availability applications on Kubernetes and AWS platforms, with a strong focus on building resilient, scalable backend systems. My work on end-to-end AI products, from data curation to model serving, has prepared me to contribute effectively to \textbf{Speechify}'s infrastructure.
	
	I am particularly drawn to Speechify's mission of aiding those with learning differences and am excited about the prospect of applying my skills to create impactful, life-changing technology.
	
	\makeletterclosing
	
\end{document}