\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{green}

\usepackage[scale=0.75]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}

% Personal data
\name{Thanh}{Hoang-Minh}
\title{Application for Senior Software Engineer Position}
\address{Ho Chi Minh City}{}{Vietnam}
\phone[mobile]{+84~913~472~506}
\email{hmthanhgm@gmail.com}
\homepage{hmthanh.github.io}

\begin{document}
	
	% Letter recipient
	\recipient{Mauritius}{Hiring Team}
	\date{\today}
	\opening{Dear Mauritius Hiring Team,}
	\closing{Thank you for your consideration.}
	\enclosure[Attachment]{Curriculum Vitae}
	\makelettertitle
	
	I am writing to apply for the \textbf{AI Engineer} position at your company. The opportunity to contribute to a next-generation HR Tech platform strongly aligns with my experience in building intelligent systems and AI-driven solutions.
	
	I have developed and deployed production-ready models using Python, and Hugging Face. My work includes fine-tuning LLMs, implementing NLP, and optimizing MLOps pipelines - directly matching your requirements for HR workflow automation and intelligent decision-making.
	
	My experience spans the full AI development lifecycle, from designing data pipelines and training models to deploying scalable cloud solutions on AWS. I have particular expertise in building ethical, compliant AI systems and thrive in dynamic startup environments where cross-functional collaboration is key.
	
	I am excited by your mission to transform HR technology and would be eager to contribute my skills in generative AI, neural networks, and cloud-native development to your platform.
	
	
	\makeletterclosing
	
\end{document}